---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.path = "man/figures/README-"
  )
```

# cryptor

## Overview

**cryptor** is an R package that wraps around the API's of Kraken, Binance and Nomics. The package can be used to access cryptocurrency-related data. To some extent, it can be used to manage a portfolio of cryptocurrencies on a centralized exchange.

The [current version](https://github.com/minornode/cryptor/releases/tag/v0.91) of the package is 0.91

## Installation

```{r, eval = FALSE}
# The easiest way to obtain the package is to install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("minornode/cryptor")
```

## Dependencies

The library comes with quite some dependencies. Installing the cryptor package should also install the following packages:

*  dplyr (>= 0.7.5),
*  tidyr (>= 0.8.1),
*  plyr (>= 1.8.4),
*  magrittr (>= 1.5),
*  httr (>= 1.3.1),
*  jsonlite (>= 1.5),
*  digest (>= 0.6.15),
*  base64enc (>= 0.1-3),
*  assertthat (>= 0.2.0.9000),
*  lubridate (>= 1.7.4),
*  data.table (>= 1.11.4)

## Usage

To use the functionality of the API's you can either call a public query (e.g. [kraken_servertime()]) or alternatively to call a private query you must first set the credentials using the appropriate function (e.g. [credentials_kraken()]).

```{r, eval = FALSE}
# All nomics endpoints require a signature
credentials_nomics(key = "2018-09-demo-dont-deploy-b69315e440beb145") # demo API key can be outdated
nomics_markets()

# Public Kraken API calls can be called without credentials
kraken_assetpairs()

# Private Kraken API calls require credentials to be set first
credentials_kraken(key = 'abcd', secret = '123')
kraken_ledger()
```

```{r plot.bitcoin, message = FALSE}
library(tidyverse)
library(cryptor)
kraken_candles(pairs = "XBTEUR", interval = 1440) %>% 
  ggplot(aes(x = time, y = close)) + 
  geom_line() + 
  theme_classic()
```

## Contribution guideline

All contributions are welcome. Feel free to add issues / PR's.

## Who do I talk to?

* You can contact me at *thibaut.vanweehaeghe@gmail.com*
* ETH adress: 0x05Aa67ce7D9a9A4Cb115d3CC5c7dbaE250eB1539
